---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# RImageJROI

The goal of RImageJROI is to read 'Fiji/ImageJ' Region of Interest (ROI) Files.

## Installation

You can install the released version of RImageJROI from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("RImageJROI")
```

or dev version

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("statnmap/RImageJROI")
```

## Example

- Read roi zip file
```{r}
library(RImageJROI)
file <- system.file("extdata", "ijroi", "ijzip.zip", package = "RImageJROI")
roi_zip <- read.ijzip(file)
```

## Transform roi as sf object

This allows to use tools made for spatial data analyses available for roi objects.
This maybe useful for image data analyses.

```{r}
roi_zip_sf <- ij_as_sf(roi_zip)
roi_zip_sf
plot(roi_zip_sf)
```

## Further documentation

Build and read the vignette included in the package.
```{r, eval=FALSE}
remotes::install_github("statnmap/RImageJROI", vignettes = TRUE)
vignette("read-roi", package = "RImageJROI")
```

